---
title: "Lab 3"
author: "Aaron Roche"
output:
  word_document: default
  pdf_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE,fig.width=6, fig.height=3,cache = FALSE)
```

## Step 1: Preliminaries


Load the mosaic and tidyverse (installed last week) packages:
```{r}
library(mosaic)
library(tidyverse)
```

We will use the NHANES dataset (nhanes.csv) that we used last week. 
Either replace the file path in the code below, or use File-> Import Dataset -> From Text (readr) and copy and paste the code that shows up in the console.
```{r}
library(readr)
nhanes <- read_csv("nhanes.csv")
View(nhanes)
```

This week we will examine the distributions of height and weight. Since these tend to be smaller for children, we will focus on adults. This code makes a new dataset, `adult`, by taking the subset of `nhanes` of subjects with `age`$\ge$`18`:
```{r}
adult <- filter(nhanes,age>=18)
```


### Problem 1
a) Make a histogram of weight in the `adult` dataset
```{r prob1a}
# gf_histogram(~weight,data = adult)
```
b) Find the mean weight in `adult`
```{r prob1b}
# 82.20044 kg
```
c) Find the median weight in `adult`
```{r prob1c}
# 78.6 kg
```
d) From the histogram and/or the mean and median of weight, do you think the 
distribution of weight is left skewed, symmetric, or right skewed? Why?
  The distribution of weight seems to be right-skewed. This is because the values on the left of the histogram a larger and they start to decrease as you move to the left side. Also, the mean and median are located on the left side of the histogram.

e) The weights here are in kilograms. To get weights in pounds, multiply by 2.2. What are the mean and median weights in pounds?
```{r prob1e}
# Mean in pounds: 180.840968 lbs
# Median in pounds: 168.96 lbs
```

f) What would be the mean and median weight if the 2014 Godzilla had been included in the dataset?
```{r prob1f}
# Mean with Godzilla: 19719.97 kg
# Median with Godzilla: 78.6 kg
```

## Problem 2
a) Compute the variance, sd, and IQR of weight in the `adult` dataset in kilograms. 
```{r prob2a}
# variance in kg: 513.0326
# sd in kg: 22.65022
# IQR in kg: 27.8
```
b) Compute the variance, sd, and IQR of weight in the `adult` dataset in pounds. 
```{r prob2b}
# variance in lbs: 1128.6717
# sd in lbs: 49.8304
# IQR in lbs: 61.16
```
c) Compute the variance, sd, and IQR of weight if Godzilla were included in the dataset? Which measure changed the most? Which changed the least?
```{r prob2c}
# variance with Godzilla (kg): 1.767398e+12
# sd with Godzilla (kg): 1329435
# IQR with Godzilla (kg): 27.8
```

d) What would be the Z-score of Godzilla's weight, if he were included in the dataset?
```{r prob2d}
# 67.6831
```


## Problem 3

a) Compute the 5-number summary for `weight` in the `adult` dataset. 
```{r prob3a}
#   0%   25%   50%   75%  100% 
# 36.8  66.4  78.6  94.2 219.6 
```


b) Use the `mean()` and `quantile()` functions to compute exactly what proportion of the weights are below the 0.1th quantile. 
```{r prob3b}
# 0.09995635
```


c) Make a boxplot of `weight`.
```{r prob3c}
# gf_boxplot(~weight, data=adult)
```



## Problem 4

a) Make a scatterplot of height vs weight
```{r prob4a}
# gf_point(height~weight,data=adult)
```

b) What is the correlation of height and weight?
```{r prob4b}
# 0.4396119
```

c) What would the corrleation be if Godzilla were in the dataset?
```{r prob4c}
# 0.9999805
```

d) How about the Spearman correlation?

```{r prob4d}
# Spearman correlation of height and weight: 0.4590817
```